Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-08-31 paper/main.tex
formulate first part of the introduction

>>>>

\acp{abm} have proven to be powerfull tools in the study of complex cellular systems.
They have been applied in various scenarios, such as cancer
research~\cite{Ghaffarizadeh2018,Cooper2020}, Immuno-Oncology~\cite{Karolak2021} or the modeling
of mechanical intercellular connections in plant cells.
By treating cells as individual entities, these tools allow researchers to think in terms of
cellular properties and processes thus allowing for a better understanding of the biological
reality.

Despite their popularity, \acp{abm} face multiple challenges in practise.
Constructing a fully working \ac{abm} simulation from scratch is an intricate process that requires
a large set of skills and time.
It is therefore common practise to reuse existing simulation tools, which brings along a number of
other problems.
Even if the existing tool is designed to be generalizable, it often comes with a pre-defined set
of parameters that need to be specified.
Furthermore, as we have discussed in our previous work~\cite{Pleyer2023}, these tools were most
often not designed to be flexible but rather for specific purposes thus limiting their
generalizability.
% TODO citations
Typically researchers aim to estimate every individual parameter of their model.
This is achieved using methods such as the profile-likelihood and model reduction techniques.
% TODO citaitons
When it comes to \acp{abm} however, it is often only shown that the results which have been
generated by an \ac{abm} lead to the phenomenon which aligns with the observed biological reality.
% TODO citations
This reduces the confidence in the constructed models and raises concerns with respect to the
validity of the obtained results.
